%-------------------------
% Resume in Latex
% Author : Harshibar (original), improved version
% Based off of: https://github.com/jakeryang/resume
% License : MIT
%------------------------
\documentclass[letterpaper,11pt]{article}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage[scale=0.90,lf]{FiraMono}
\usepackage{tgheros}
\renewcommand*\familydefault{\sfdefault}
\usepackage[T1]{fontenc}

\definecolor{light-grey}{gray}{0.83}
\definecolor{dark-grey}{gray}{0.3}
\definecolor{text-grey}{gray}{.08}

\pagestyle{fancy}
\fancyhf{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{0in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section{\Large}{
  \bfseries \vspace{2pt} \raggedright \large
}{}{0em}{}[\color{light-grey}{\titlerule[2pt]} \vspace{-4pt}]

\newcommand{\resumeItem}[1]{
  \item\small{{#1 \vspace{-1pt}}}
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & {\color{dark-grey}\small #2}\vspace{1pt}\\
      \textit{#3} & {\color{dark-grey}\small #4}\\
    \end{tabular*}\vspace{-4pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{0pt}}

\color{text-grey}

\begin{document}

%----------HEADING----------
\begin{center}
    \textbf{\Huge Twinkal Meshram} \\[6pt]
    \textbf{\Large Security Analyst} \\[10pt]
   
    \small
    \faPhone*\hspace{4pt}\texttt{+91 9156495158} \quad $|$\quad
    \href{mailto:meshramtwinkal@gmail.com}{\faEnvelope\hspace{6pt}\texttt{meshramtwinkal@gmail.com}} \quad $|$\quad
    \href{https://www.linkedin.com/in/twinkalmeshram2}{\faLinkedin\hspace{6pt}\texttt{twinkalmeshram2}} \quad $|$\quad
    \href{https://github.com/twinkal358}{\faGithub\hspace{6pt}\texttt{twinkal358}}
   
    \vspace{6pt}
\end{center}

% Professional Summary
\section{\Large{\Large PROFESSIONAL SUMMARY}
Dedicated Vulnerability Management and Cyber Threat Intelligence specialist with 2+ years of experience securing large-scale telecommunications and enterprise IT environments (including IBM and HDFC clients). Expert in end-to-end vulnerability lifecycle using Qualys VMDR — from scanning and CVSS-based prioritization to remediation coordination and executive risk reporting. Skilled in Forcepoint DLP, SIEM (QRadar), threat intelligence platforms (Cyware, Recorded Future), and endpoint protection tools. Proven track record of reducing risk exposure, eliminating false positives, and enabling proactive threat mitigation.

% Education
\section{\Large{EDUCATION}
\resumeSubHeadingListStart
    \resumeSubheading
      {Government College of Engineering \& Research, Avasari Khurd}
      {Pune, Maharashtra}
      {B.E. in Computer Engineering \textbullet\ 8.36 CGPA}
      {2019 -- 2023}
\resumeSubHeadingListEnd

% Technical Skills
\section{\Large{TECHNICAL SKILLS}
\begin{itemize}[leftmargin=*]
  \item \textbf{Vulnerability Management}: Qualys VMDR (asset grouping, scan orchestration, CVSS / risk scoring, false-positive validation, patch coordination)
  \item \textbf{Security Operations \& Monitoring}: Forcepoint DLP, IBM QRadar SIEM, Cyware, Recorded Future, Remedy, Flexera
  \item \textbf{Endpoint Protection}: Symantec Endpoint Manager (SEPM), Trend Micro Deep Security, Trellix-HX (EDR)
  \item \textbf{Penetration Testing \& Tools}: Nmap, Burp Suite, Metasploit, Wireshark, Searchsploit, Exploit-DB, Checkmarx
  \item \textbf{Programming Languages \& Scripting}: Python, C++, PHP, MySQL, HTML/CSS, Bootstrap
  \item \textbf{Platforms and Operating Systems}: Windows, Ubuntu, Kali Linux
\end{itemize}

%-----------EXPERIENCE-----------
\section{\Large{PROFESSIONAL EXPERIENCE}
\resumeSubHeadingListStart
  \resumeSubheading
    {Technical Support Representative — Vulnerability Management}
    {Mar 2024 -- Present}
    {IBM India Pvt Ltd (Client: HDFC)}
    {Navi Mumbai, India}
    \resumeItemListStart
        \resumeItem{Executed enterprise-wide vulnerability scanning using Qualys VMDR across thousands of assets, maintaining continuous visibility and compliance.}
        \resumeItem{Prioritized remediation by CVSS scoring + business risk context, reducing critical exposure and focusing engineering efforts on high-impact items.}
        \resumeItem{Eliminated false positives through rigorous validation, decreasing remediation noise by significant margin and accelerating mean-time-to-remediate.}
        \resumeItem{Coordinated patch deployment and closure verification across cross-functional teams, achieving consistent SLA adherence.}
        \resumeItem{Developed executive vulnerability dashboards and risk posture reports, enabling data-driven security investment decisions.}
    \resumeItemListEnd

  \resumeSubheading
    {Cyber Threat Intelligence \& DLP Incident Analyst}
    {Oct 2023 -- Feb 2024}
    {Outworks Solutions Pvt Ltd (Client: IBM / Vodafone Idea)}
    {Pune, India}
    \resumeItemListStart
        \resumeItem{Tracked and disseminated high-priority threat intelligence using Cyware and Recorded Future, enabling proactive mitigation of telecom-sector threats.}
        \resumeItem{Blocked malicious IOCs at scale and enriched threat data, strengthening defensive controls against emerging campaigns.}
        \resumeItem{Performed proactive threat hunting; identified and reported novel indicators to CERT-In, contributing to national-level visibility.}
        \resumeItem{Monitored and investigated potential data-exfiltration events via Forcepoint DLP + QRadar, ensuring rapid containment for VIP / sensitive accounts.}
    \resumeItemListEnd

  \resumeSubheading
    {Endpoint Security Analyst}
    {Dec 2022 -- Sep 2023}
    {Outworks Solutions Pvt Ltd}
    {Pune, India}
    \resumeItemListStart
        \resumeItem{Managed Symantec SEPM, Trend Micro Deep Security, and Trellix-HX across enterprise endpoints; maintained high detection efficacy.}
        \resumeItem{Conducted daily security posture reviews and tuned detection rules, reducing alert fatigue and improving threat visibility.}
        \resumeItem{Analyzed malware events and produced infection-risk reports for critical servers, driving targeted remediation.}
        \resumeItem{Remediated non-compliant hosts via automated Host Integrity checks, increasing endpoint compliance rates.}
    \resumeItemListEnd
\resumeSubHeadingListEnd

\section{\Large{CERTIFICATIONS}
\resumeSubHeadingListStart
    \resumeItem{Qualys Certified Specialist}
    \resumeItem{Certified Forcepoint DLP Administrator}
    \resumeItem{Trend Micro Deep Security 20 Technical Essentials}
    \resumeItem{Cyber Shiksha (DSCI \& Microsoft)}
    \resumeItem{Think Like a Hacker}
    \resumeItem{Gen AI Exchange Hackathon 2025 (Google Cloud)}
    \resumeItem{Python for Data Science (IBM)}
    \resumeItem{AI \& Web Development (Microsoft)}
\resumeSubHeadingListEnd

\section{\Large{AWARDS \& RECOGNITIONS}
\resumeSubHeadingListStart
    \resumeSubheading{Client Appreciation Award for Best Performer}
    {Jul 2024}
    {IBM / Outworks}
    {}
\resumeSubHeadingListEnd

\section{\Large{POSITIONS OF RESPONSIBILITY}
\resumeSubHeadingListStart
    \resumeSubheading{ERC Club Member}
    {}
    {Government College of Engineering \& Research, Avasari}
    {}
    \resumeItemListStart
        \resumeItem{Led web development initiatives and handled HR coordination under tight deadlines.}
    \resumeItemListEnd
\resumeSubHeadingListEnd

\end{document}